Student Replication for \"Money Illusion\

### 2024-02-10 outputs/paper/paper.qmd
uploaded dataset

---
title: "A Modest Proposal for Developing Better Experience with TTC Subway"
title-block-banner: true
abstract: ""
thanks: "Code and data supporting this analysis are available at: https://github.com/TEJMaster/Student-Replication-For-Money-Illusion.git"
author: "Terry Tu"
date: today
date-format: long
format: pdf
toc: true
toc-depth: 1
number-sections: true
bibliography: references.bib
link-citations: true
---

>>>>

---
title: "Student Replication for \"Money Illusion\""
title-block-banner: true
abstract: ""
thanks: "Code and data supporting this analysis are available at: https://github.com/TEJMaster/Student-Replication-For-Money-Illusion.git"
author: "Terry Tu, Jingyi Shen, Yaning Jin "
date: today
date-format: long
format: pdf
toc: true
toc-depth: 1
number-sections: true
bibliography: references.bib
link-citations: true
---
